Trawl Summary

### 2020-08-10 text/trawl_summary.Rmd
initiate the LDATS analysis
updating the trawl summary
updated salinity and temp files and

#TERREBONNE BAY TRAWL ANALYSIS SUMMARY {.unlisted .unnumbered}

@@

>>>>

# TERREBONNE BAY TRAWL ANALYSIS SUMMARY {.unlisted .unnumbered}

@@

## LDATS

This is the beginning of the LDATS summary

```{r LDATS, echo = FALSE, warning=FALSE, include = TRUE, fig.height=8, fig.width=10}
library(LDATS)
trawl_LDATS <- readRDS(file = "../data/TB_trawl_LDATS.rds")
plot(trawl_LDATS)
```
